---
title: "OMOP Common Data Model Specifications"
author: Christian Reich, Patrick Ryan, Rimma Belenkaya, Karthik Natarajan and Clair
  Blacketer
date: "`r Sys.Date()`"
output:
  html_document:
    df_print: paged
    toc: yes
  pdf_document:
    latex_engine: xelatex
    number_sections: yes
    toc: yes
linkcolor: blue
params:
  mdFilesLocation: S:/Git/GitHub/CommonDataModel.wiki
keep-tex: yes
---

```{r, echo=FALSE}
mdFilesLocation <- params$mdFilesLocation
```

# License
```{r child = paste0(mdFilesLocation,'/License.md')}
```

# Background
```{r child = paste0(mdFilesLocation,'/Background/Background.md')}
```

## The Role of the Common Data Model
```{r child = paste0(mdFilesLocation,'/Background/The-Role-of-the-Common-Data-Model.md')}
```

## Design Principles
```{r child = paste0(mdFilesLocation,'/Background/Design-Principles.md')}
```

## Data Model Conventions
```{r child = paste0(mdFilesLocation,'/Background/Data-Model-Conventions.md')}
```

# Glossary of Terms
```{r child = paste0(mdFilesLocation,'/Glossary-of-Terms.md')}
```

# Standardized Vocabularies
```{r child = paste0(mdFilesLocation,'/StandardizedVocabularies/Standardized-Vocabularies.md')}
```

## CONCEPT
```{r child = paste0(mdFilesLocation,'/StandardizedVocabularies/CONCEPT.md')}
```

## VOCABULARY
```{r child = paste0(mdFilesLocation,'/StandardizedVocabularies/VOCABULARY.md')}
```

## DOMAIN
```{r child = paste0(mdFilesLocation,'/StandardizedVocabularies/DOMAIN.md')}
```

## CONCEPT_CLASS
```{r child = paste0(mdFilesLocation,'/StandardizedVocabularies/CONCEPT_CLASS.md')}
```

## CONCEPT_RELATIONSHIP
```{r child = paste0(mdFilesLocation,'/StandardizedVocabularies/CONCEPT_RELATIONSHIP.md')}
```

## RELATIONSHIP
```{r child = paste0(mdFilesLocation,'/StandardizedVocabularies/RELATIONSHIP.md')}
```

## CONCEPT_SYNONYM
```{r child = paste0(mdFilesLocation,'/StandardizedVocabularies/CONCEPT_SYNONYM.md')}
```

## CONCEPT_ANCESTOR
```{r child = paste0(mdFilesLocation,'/StandardizedVocabularies/CONCEPT_ANCESTOR.md')}
```

## SOURCE_TO_CONCEPT_MAP
```{r child = paste0(mdFilesLocation,'/StandardizedVocabularies/SOURCE_TO_CONCEPT_MAP.md')}
```

## DRUG_STRENGTH
```{r child = paste0(mdFilesLocation,'/StandardizedVocabularies/DRUG_STRENGTH.md')}
```

# Standardized Metadata
```{r child = paste0(mdFilesLocation,'/StandardizedMetadata/Standardized-Metadata.md')}
```

## CDM_SOURCE
```{r child = paste0(mdFilesLocation,'/StandardizedMetadata/CDM_SOURCE.md')}
```

## METADATA
```{r child = paste0(mdFilesLocation,'/StandardizedMetadata/METADATA.md')}
```

# Standardized Clinical Data Tables
```{r child = paste0(mdFilesLocation,'/StandardizedclinicalDataTables/Standardized-clinical-Data-Tables.md')}
```

## PERSON
```{r child = paste0(mdFilesLocation,'/StandardizedclinicalDataTables/PERSON.md')}
```

<!-- ## OBSERVATION_PERIOD -->
<!-- ```{r child = paste0(mdFilesLocation,'/StandardizedclinicalDataTables/OBSERVATION_PERIOD.md')} -->
<!-- ``` -->

<!-- ## VISIT_OCCURRENCE -->
<!-- ```{r child = paste0(mdFilesLocation,'/StandardizedclinicalDataTables/VISIT_OCCURRENCE.md')} -->
<!-- ``` -->

<!-- ## VISIT_DETAIL -->
<!-- ```{r child = paste0(mdFilesLocation,'/StandardizedclinicalDataTables/VISIT_DETAIL.md')} -->
<!-- ``` -->

<!-- ## CONDITION_OCCURRENCE -->
<!-- ```{r child = paste0(mdFilesLocation,'/StandardizedclinicalDataTables/CONDITION_OCCURRENCE.md')} -->
<!-- ``` -->

<!-- ## DEATH -->
<!-- ```{r child = paste0(mdFilesLocation,'/StandardizedclinicalDataTables/DEATH.md')} -->
<!-- ``` -->

<!-- ## DRUG_EXPOSURE -->
<!-- ```{r child = paste0(mdFilesLocation,'/StandardizedclinicalDataTables/DRUG_EXPOSURE.md')} -->
<!-- ``` -->

<!-- ## PROCEDURE_OCCURRENCE -->
<!-- ```{r child = paste0(mdFilesLocation,'/StandardizedclinicalDataTables/PROCEDURE_OCCURRENCE.md')} -->
<!-- ``` -->

<!-- ## DEVICE_EXPOSURE -->
<!-- ```{r child = paste0(mdFilesLocation,'/StandardizedclinicalDataTables/DEVICE_EXPOSURE.md')} -->
<!-- ``` -->

<!-- ## MEASUREMENT -->
<!-- ```{r child = paste0(mdFilesLocation,'/StandardizedclinicalDataTables/MEASUREMENT.md')} -->
<!-- ``` -->

<!-- ## NOTE -->
<!-- ```{r child = paste0(mdFilesLocation,'/StandardizedclinicalDataTables/NOTE.md')} -->
<!-- ``` -->

<!-- ## NOTE_NLP -->
<!-- ```{r child = paste0(mdFilesLocation,'/StandardizedclinicalDataTables/NOTE_NLP.md')} -->
<!-- ``` -->

<!-- ## SURVEY_CONDUCT -->
<!-- ```{r child = paste0(mdFilesLocation,'/StandardizedclinicalDataTables/SURVEY_CONDUCT.md')} -->
<!-- ``` -->

<!-- ## OBSERVATION -->
<!-- ```{r child = paste0(mdFilesLocation,'/StandardizedclinicalDataTables/OBSERVATION.md')} -->
<!-- ``` -->

<!-- ## SPECIMEN -->
<!-- ```{r child = paste0(mdFilesLocation,'/StandardizedclinicalDataTables/SPECIMEN.md')} -->
<!-- ``` -->

<!-- ## FACT_RELATIONSHIP -->
<!-- ```{r child = paste0(mdFilesLocation,'/StandardizedclinicalDataTables/FACT_RELATIONSHIP.md')} -->
<!-- ``` -->

<!-- # Standardized Health System Data Tables -->
<!-- ```{r child = paste0(mdFilesLocation,'/StandardizedHealthSystemDataTables/Standardized-Health-System-Data-Tables.md')} -->
<!-- ``` -->

<!-- ## LOCATION -->
<!-- ```{r child = paste0(mdFilesLocation,'/StandardizedHealthSystemDataTables/LOCATION.md')} -->
<!-- ``` -->

<!-- ## LOCATION_HISTORY -->
<!-- ```{r child = paste0(mdFilesLocation,'/StandardizedHealthSystemDataTables/LOCATION_HISTORY.md')} -->
<!-- ``` -->

<!-- ## CARE_SITE -->
<!-- ```{r child = paste0(mdFilesLocation,'/StandardizedHealthSystemDataTables/CARE_SITE.md')} -->
<!-- ``` -->

<!-- ## PROVIDER -->
<!-- ```{r child = paste0(mdFilesLocation,'/StandardizedHealthSystemDataTables/PROVIDER.md')} -->
<!-- ``` -->

<!-- # Standardized Health Economics Data Tables -->
<!-- ```{r child = paste0(mdFilesLocation,'/StandardizedHealthEconomicsDataTables/Standardized-Health-Economics-Data-Tables.md')} -->
<!-- ``` -->

<!-- ## PAYER_PLAN_PERIOD -->
<!-- ```{r child = paste0(mdFilesLocation,'/StandardizedHealthEconomicsDataTables/PAYER_PLAN_PERIOD.md')} -->
<!-- ``` -->

<!-- ## COST -->
<!-- ```{r child = paste0(mdFilesLocation,'/StandardizedHealthEconomicsDataTables/COST.md')} -->
<!-- ``` -->

<!-- # Standardized Derived Elements -->
<!-- ```{r child = paste0(mdFilesLocation,'/StandardizedDerivedElements/Standardized-Derived-Elements.md')} -->
<!-- ``` -->

<!-- ## DRUG_ERA -->
<!-- ```{r child = paste0(mdFilesLocation,'/StandardizedDerivedElements/DRUG_ERA.md')} -->
<!-- ``` -->

<!-- ## DOSE_ERA -->
<!-- ```{r child = paste0(mdFilesLocation,'/StandardizedDerivedElements/DOSE_ERA.md')} -->
<!-- ``` -->

<!-- ## CONDITION_ERA -->
<!-- ```{r child = paste0(mdFilesLocation,'/StandardizedDerivedElements/CONDITION_ERA.md')} -->
<!-- ``` -->

<!-- # Results Schema -->
<!-- ```{r child = paste0(mdFilesLocation,'/ResultsSchema/Results-Schema.md')} -->
<!-- ``` -->

<!-- ## COHORT -->
<!-- ```{r child = paste0(mdFilesLocation,'/ResultsSchema/COHORT.md')} -->
<!-- ``` -->

<!-- ## COHORT_DEFINITION -->
<!-- ```{r child = paste0(mdFilesLocation,'/ResultsSchema/COHORT_DEFINITION.md')} -->
<!-- ``` -->
